Gamification Effectiveness on Education

### 2024-04-17 paper/paper.qmd
explain the table model results

# Results

Our results are summarized in @tbl-modelresults.

@@

first_model <-
  readRDS(file = here::here("models/final_exam.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

## First discussion point

@@

## Second discussion point

## Third discussion point

@@

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

>>>>

# Results
Our results are summarized in @tbl-modelresults. Social gamification group grades are almost comparable to the control group as on average they tend to be lower by 1-2%. While, a student in the educational game group, their grades on average are 6-7% lower than the control group. And then, a student in social network group, their grades on average 11-12% lower than the control group. Lastly, a student in the gamification plugin group, their grades on average are 15-16% lower than the control group.

@@

finalExam_model <-
  readRDS(file = here::here("models/final_exam.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of Final Exam marks based off of the experiment group and gender"
#| warning: false

modelsummary::modelsummary(
  list(
    "Final Exam Marks" = finalExam_model
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

## Design of Gamification

@@

## Good example of Gamification

## Student's opinon about it

@@

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]

plot(finalExam_model, "trace")

plot(finalExam_model, "rhat")
```
